### 2024-03-24 content/chapter_1.tex
:pencil: Add BackCom introduction and MCS
:pencil: Add abstract and BackCom applications

	One promising candidate within this 6G vision is \gls{ris}, a programmable metasurface that recycles and redistributes the electromagnetic waves in the air for improved wireless performance.
	It could be incorporated into the transmitter and receiver for \emph{beamforming}, employed as a free-rider information source for \emph{modulation}, or simply placed in space as a standalone device for \emph{channel shaping}.
	These applications have distinctive requirements and trade-offs, but the operation principles are the same and those roles are not mutually exclusive.
	Imagine a future where everything can be ``smartened'' by coating with a metamaterial layer and attaching a microcontroller tag.
	Only a few active radiating sources (like the sun) are needed, while most objects (like the universe) can exploit the surrounding waves to energize themselves, sense the environment, communicate with others, and help those in need when idle.
	This vision motivates three research questions to be addressed in this thesis:
	\begin{itemize}
		\item \emph{How does \gls{ris} impact different wireless applications such as communication and far-field power transfer?}
		\item \emph{Is it possible to integrate \gls{ris} with \gls{bc} into a versatile tool that blurs the boundary between the network and environment?}
		\item \emph{What is the ultimate limit of channel reshaping through passive \gls{ris} and what are the implications on transceiver designs?}
	\end{itemize}

	Before delving into these questions, we first provide a short overview of \gls{ris} and introduce some potential applications.
	A detailed literature review and technical discussion on \gls{ris} and other topics will be reserved for Chapter \ref{ch:background}.
\end{section}

@@

	\begin{subsection}{Concept}
		\gls{ris} is commonly known as a planar surface involving numerous wave scattering elements (a.k.a. unit cells, reflective patches), whose amplitude and phase responses can be engineered in real-time to achieve a desired radiation pattern.
		It behaves like a delicate \gls{rf} mirror with adjustable curvature and orientation, which allows the incident signals to be focused and redirected in a particular direction.
		As shown in Fig. \ref{fg:ris_architecture}, its typical architecture consists of three stacked layers and a controller \cite{Wu2020}.
		The top layer is a two-dimensional array of scattering elements printed on a dielectric substrate.
		The elements directly interact with the impinging waves, which are usually fabricated from metamaterial or patch/dipole antennas with sub-wavelength dimension and spacing.
		The middle layer is a copper ground plate that provides voltage reference and avoids signal leakage.
		The bottom later is a circuit board that associate each element with adjustable components, such as varactor and \gls{pin} diodes \cite{Dai2020}.
		It also hosts a \gls{fpga} controller that controls the circuit and coordinate with transceivers in the network.
		By adjusting the scatter response of all elements, the \gls{ris} can effectively manipulate the wavefront for a constructive or destructive superposition and thus improve the ambient wireless environment.
		\begin{figure}
			\centering
			\includegraphics[width=0.9\textwidth]{ris_architecture.pdf}
			\caption{A typical architecture of \gls{ris}. The figure is modified from \cite{Wu2020}.}
			\label{fg:ris_architecture}
		\end{figure}
	\end{subsection}

@@

		\item Chapter \ref{ch:introduction} provides an overview of the thesis. It introduces the motivation and objectives, discusses the characteristics and applications of \gls{ris}, and summarizes the topics and contributions of each research chapter. A list of publications is also provided.
		\item Chapter \ref{ch:background} provides the necessary background knowledge for the subsequent chapters, including the fundamental principles, hardware implementation, signal and system models, performance metrics, and design challenges for \gls{ris}, \gls{wpt}, \gls{swipt}, \gls{bc}, and \gls{mimo} systems. It also reviews the state-of-the-art research in relevant topics and raise critical questions to be addressed in the following chapters.

>>>>

	One promising candidate within this 6G vision is \gls{ris}, a programmable metasurface that recycles and redistributes the electromagnetic waves in the air for improved wireless performance.
	It could be incorporated into the transmitter and receiver for \emph{beamforming}, employed as a free-rider information source for \emph{modulation}, or simply placed in space as a standalone device for \emph{channel shaping}.
	These applications have distinctive requirements and trade-offs, but the operation principles are the same and those roles are not mutually exclusive.
	Imagine a future where everything can be ``smartened'' by coating with a metamaterial layer and attaching a microcontroller tag.
	Only a few active radiating sources (like the sun) are needed, while most objects (like the universe) can exploit the surrounding waves to energize themselves, sense the environment, communicate with others, and help those in need when idle.
	This vision motivates three research questions to be addressed in this thesis:
	\begin{itemize}
		\item \emph{How does \gls{ris} impact different wireless applications such as communication and far-field power transfer?}
		\item \emph{Is it possible to integrate \gls{ris} with other scattering applications into a versatile tool that blurs the boundary between the network and environment?}
		\item \emph{What is the ultimate limit of channel reshaping through passive \gls{ris} and what are the implications on transceiver designs?}
	\end{itemize}

	Before delving into these questions, we first provide a short overview of \gls{ris} and introduce some potential applications.
	A detailed literature review and technical discussion on \gls{ris} and other technologies will be reserved for Chapter \ref{ch:background}.
\end{section}

@@

	\begin{subsection}{Concept}
		\gls{ris} is commonly known as a planar surface involving numerous wave scattering elements (a.k.a. unit cells, reflective patches), whose amplitude and phase responses can be engineered in real-time to achieve a desired radiation pattern.
		It behaves like a delicate \gls{rf} mirror with adjustable curvature and orientation, which allows the incident signals to be focused and redirected in a particular direction.
		As shown in Fig. \ref{fg:ris_architecture}, its typical architecture consists of three stacked layers and a controller \cite{Wu2020}.
		The top layer is a two-dimensional array of scattering elements printed on a dielectric substrate.
		The elements directly interact with the impinging waves, which are usually fabricated from metamaterial or patch/dipole antennas with sub-wavelength dimension and spacing.
		The middle layer is a copper ground plate that provides voltage reference and avoids signal leakage.
		The bottom later is a circuit board that associate each element with adjustable components, such as varactor and \gls{pin} diodes \cite{Dai2020}.
		It also hosts a \gls{fpga} controller that controls the circuit and coordinate with transceivers in the network.
		By adjusting the scatter response of all elements, the \gls{ris} can effectively manipulate the wavefront for a constructive or destructive superposition and thus improve the ambient wireless environment.
		\begin{figure}
			\centering
			\includegraphics[width=0.9\textwidth]{ris_architecture.pdf}
			\caption{A typical architecture of \gls{ris}. Source: Modified from \cite{Wu2020}.}
			\label{fg:ris_architecture}
		\end{figure}
	\end{subsection}

@@

		\item Chapter \ref{ch:introduction} provides an overview of the thesis. It introduces the motivation and objectives, raise critical research questions, discusses the characteristics and applications of \gls{ris}, and summarizes the contributions of each research chapter. A list of publications is also provided.
		\item Chapter \ref{ch:background} provides necessary background knowledge for \gls{ris}, \gls{wpt}, \gls{swipt}, and \gls{bc}. It covers fundamental principles, hardware implementation, signal and system models, performance metrics, design challenges, and state-of-the-art research.

### 2024-03-24 content/chapter_2.tex
:pencil: Add abstract and BackCom applications

@@

	\begin{subsection}{Modules and Operation Modes}
		\begin{subsubsection}{Information and Energy Flows}
			In \gls{swipt}, the information and energy are always transmitted from the same source while their receivers can be either co-located or separated, as shown in Figs. \subref*{fg:swipt_colocated} and \subref*{fg:swipt_separated}.
			This is different from \gls{bc} where the energy is delivered in the downlink and the information is sent in the uplink, as shown in Figs. \subref*{fg:backcom_monostatic} and \subref*{fg:backcom_bistatic}.
			\begin{figure}[H]
				\centering
				\subfloat[\gls{swipt} with co-located receiver]{
					\resizebox{7cm}{!}{
						\input{assets/chapter_2/swipt_colocated.tex}
					}
					\label{fg:swipt_colocated}
				}
				\subfloat[\gls{swipt} with separated receivers]{
					\resizebox{7cm}{!}{
						\input{assets/chapter_2/swipt_separated.tex}
					}
					\label{fg:swipt_separated}
				}
				\\
				\subfloat[Monostatic backscatter]{
					\resizebox{7cm}{!}{
						\input{assets/chapter_2/backcom_monostatic.tex}
					}
					\label{fg:backcom_monostatic}
				}
				\subfloat[Bistatic backscatter]{
					\resizebox{7cm}{!}{
						\input{assets/chapter_2/backcom_bistatic.tex}
					}
					\label{fg:backcom_bistatic}
				}
				\caption{
					Information and energy flows in \gls{swipt} and \gls{bc} systems. Blue and black parts denote information and power subsystems, respectively.
				}
				\label{fg:wipt_schemes}
			\end{figure}
			From a design perspective, co-located \gls{swipt} receiver is a more general model since it can exploit the received signal for either purpose or a mixture in between.
			We thus focus on this model in the following context.
		\end{subsubsection}

@@

	\begin{subsection}{Applications}
		\begin{subsubsection}{\glsfmtfull{mbc}}

		\end{subsubsection}

		\begin{subsubsection}{\glsfmtfull{bbc}}

		\end{subsubsection}

		\begin{subsubsection}{\glsfmtfull{ambc}}

		\end{subsubsection}

		\begin{subsubsection}{\glsfmtfull{sr}}

		\end{subsubsection}
	\end{subsection}
\end{section}

>>>>

This chapter provides essential background for topics covered in the thesis. A detailed literature review will be presented within each research chapter.

@@

	\begin{subsection}{Modules and Operation Modes}
		\begin{subsubsection}{Information and Energy Flows}
			In \gls{swipt}, the information and energy are always transmitted from the same source while their receivers can be either co-located or separated, as shown in Figs. \subref*{fg:swipt_colocated} and \subref*{fg:swipt_separated}.
			This is different from \gls{bc} where the energy is delivered in the downlink and the information is sent in the uplink, as shown in Figs. \subref*{fg:backcom_monostatic} and \subref*{fg:backcom_bistatic}.
			\begin{figure}[H]
				\centering
				\subfloat[\gls{swipt} with co-located receiver]{
					\resizebox{7cm}{!}{
						\input{assets/chapter_2/swipt_colocated.tex}
					}
					\label{fg:swipt_colocated}
				}
				\subfloat[\gls{swipt} with separated receivers]{
					\resizebox{7cm}{!}{
						\input{assets/chapter_2/swipt_separated.tex}
					}
					\label{fg:swipt_separated}
				}
				\\
				\subfloat[Monostatic backscatter]{
					\resizebox{7cm}{!}{
						\input{assets/chapter_2/backcom_monostatic.tex}
					}
					\label{fg:backcom_monostatic}
				}
				\subfloat[Bistatic backscatter]{
					\resizebox{7cm}{!}{
						\input{assets/chapter_2/backcom_bistatic.tex}
					}
					\label{fg:backcom_bistatic}
				}
				\caption{
					Information and energy flows in \gls{swipt} and \gls{bc} systems. The blue and black parts denote information and power subsystems, respectively.
				}
				\label{fg:wipt_schemes}
			\end{figure}
			From a design perspective, co-located \gls{swipt} receiver is a more general model since it can exploit the received signal for either purpose or a mixture in between.
			We thus focus on this model in the following context.
		\end{subsubsection}

@@

	\begin{subsection}{Applications}
		\begin{figure}[!t]
			\centering
			\subfloat[Monostatic backscatter]{
				\resizebox{0.48\linewidth}{!}{
					\input{assets/chapter_2/mbc.tex}
				}
				\label{fg:mbc}
			}
			\subfloat[Bistatic backscatter]{
				\resizebox{0.48\linewidth}{!}{
					\input{assets/chapter_2/bbc.tex}
				}
				\label{fg:bbc}
			}
			\\
			\subfloat[Ambient backscatter]{
				\resizebox{0.48\linewidth}{!}{
					\input{assets/chapter_2/ambc.tex}
				}
				\label{fg:ambc}
			}
			\subfloat[Symbiotic radio]{
				\resizebox{0.48\linewidth}{!}{
					\input{assets/chapter_2/sr.tex}
				}
				\label{fg:sr}
			}
			\caption{
				Illustration of scattering applications.
				The blue flows denote the primary link while the magenta flows denote the backscatter link.
			}
		\end{figure}

		\begin{subsubsection}{\glsfmtfull{mbc}}
			\gls{mbc} is the most common architecture where the carrier emitter and reader are integrated into one device called interrogator.
			As shown in \subref*{fg:backcom_monostatic} and \subref*{fg:mbc}, the interrogator transmits a \gls{cw} in the downlink and receives the reflected information-bearing signal in the uplink.
			The node varies its load impedance over time to switch between two states.
			Ideally, a full absorption (perfect matching, $\Gamma_0 = 0$) maps to bit ``0'' where energy is harvested, and a full reflection (perfect mismatch, $\lvert \Gamma_1 \rvert = 1$) maps to bit ``1'' where \gls{snr} is determined.
			\gls{mbc} is widely used in \gls{rfid} systems.
			The integrated transceiver design reduces the hardware cost but suffers from strong self-interference and limited coverage.
		\end{subsubsection}

		\begin{subsubsection}{\glsfmtfull{bbc}}
			\gls{bbc} separates the carrier emitter and reader into two individual devices, as illustrated in \subref*{fg:backcom_bistatic} and \subref*{fg:bbc}.
			This helps to combat self-interference and extend the operation range, but the system involves three devices and requires more complex coordination and synchronization.
			It is more popular in more complicated scenarios like \gls{wsn} and \gls{iot} with potentially moving nodes.
		\end{subsubsection}

		\begin{subsubsection}{\glsfmtfull{ambc}}
			\gls{ambc} has been recognized as a revolutionary technology since its debut in 2013 \cite{Liu2013b}.
			As shown in \subref*{fg:ambc}, it gets rid of dedicated \gls{rf} sources and relies on ambient signals (e.g., TV, FM, and Wi-Fi) for both energy harvesting and information transfer.
			Compared with \gls{mbc} and \gls{bbc}, its carrier waveform is no longer a \gls{cw} but a mixture of already modulated signals with different frequencies and amplitudes, which makes the detection more challenging.
			Therefore, it often employs \gls{fsk} modulation to shift the scattered signals to a different band for reduced interference on both coexisting systems.
			\gls{ambc} is a plug-and-play and environmental-friendly \gls{iot} solution, but its practical deployment is limited by the availability and quality of ambient signals.
		\end{subsubsection}

		\begin{subsubsection}{\glsfmtfull{sr}}
			\gls{sr} is a relatively new concept proposed in 2019 that introduced itself as ``cooperative \gls{ambc}'' \cite{Guo2019b}.
			As shown in \subref*{fg:sr}, it shares not only the transmitter, \gls{rf} source, but also the receiver with a primary transmission.
			This is different from traditional \gls{ambc} where the legacy system can be unaware of the backscatter link and the node wants to minimize its footprint.
			Such a symbiotic interaction can improve the reliability of the backscatter link as well as the energy efficiency of the primary link, but unavoidably challenges the system design.
			For example, the acquisition of backscatter \gls{csi} can be difficult due to its passive characteristic, the detection of node message may involve complicated signal processing like \gls{sic}, and the synchronization of both links can be nontrivial due to the load-switching constraints.
			If those issues can be mitigated, \gls{sr} would be a win-win solution that supercharges resource-constrained devices by leveraging the existing network infrastructure.
		\end{subsubsection}
	\end{subsection}
\end{section}

### 2024-03-24 content/declaration.tex
:pencil: Add abstract and BackCom applications

\begin{declaration}

I hereby declare that the contents presented in this dissertation are original and have been carried out by myself under the guidance of my supervisor Prof. Bruno Clerckx.
Any work from other researchers, scholars, or sources have been properly cited and acknowledged.
Figures, tables, and results presented in this dissertation are generated by myself, unless otherwise stated.
I would like to acknowledge the use of large language models for assistance in improving the clarity and readability of introduction and background sections of this thesis.
The contents have not been submitted in whole or in part for consideration of any other degree or qualification in any academic institution.
I am aware of the ethical standards and academic integrity policies of Imperial College London, and I have adhered to these principles throughout the course of study.
In signing this declaration, I affirm my commitment to academic honesty, intellectual integrity, and the pursuit of knowledge in the service of truth and understanding.

@@

The source code of all simulation results in this dissertation are publicly available at \url{https://github.com/snowztail/}.

\end{declaration}

>>>>

\begin{declaration}
	The contents presented in this dissertation are original and have been carried out by myself under the guidance of my supervisor Prof. Bruno Clerckx.
	Any work from other researchers, scholars, or sources have been properly cited and acknowledged.
	Figures, tables, and results presented in this dissertation are generated by myself, unless otherwise stated.
	I would like to acknowledge the use of large language models for assistance in improving the clarity and readability of introduction and background sections of this thesis.
	The contents have not been submitted in whole or in part for consideration of any other degree or qualification in any academic institution.
	I am aware of the ethical standards and academic integrity policies of Imperial College London, and I have adhered to these principles throughout the course of study.
	In signing this declaration, I affirm my commitment to academic honesty, intellectual integrity, and the pursuit of knowledge in the service of truth and understanding.

@@

	Any comments, suggestions, or corrections are greatly acknowledged and can be sent to \href{mailto:i@snowztail.com}{\url{i@snowztail.com}}.
	The source code of all simulation results in this dissertation are publicly available at \url{https://github.com/snowztail/}.
	Finally, I would like to appreciate Bruno, my colleagues, and whoever is reading this dissertation.
\end{declaration}
